Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
Gosh, i think I figured out how they calculated their stuff in the garcia borda de agua paper.

knitr::kable(qtable_models)
```

@@

```{r fig.width=9}
data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
  bind_rows(., data.frame(grid_points = pp.shape.kde$grid_points, values = pp.shape.kde$values, model = "PP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = np.shape.kde$grid_points, values = np.shape.kde$values, model = "NP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = cp.scale.kde$grid_points, values = cp.scale.kde$values, model = "CP", param = "scale") %>% 
  bind_rows(., data.frame(grid_points = pp.scale.kde$grid_points, values = pp.scale.kde$values, model = "PP", param = "scale")) %>% 
  bind_rows(., data.frame(grid_points = np.scale.kde$grid_points, values = np.scale.kde$values, model = "NP", param = "scale"))) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) -> kerneldata

@@

>>>>

qtable_models
```

@@

```{r fig.width=10}
data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
  bind_rows(., data.frame(grid_points = pp.shape.kde$grid_points, values = pp.shape.kde$values, model = "PP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = np.shape.kde$grid_points, values = np.shape.kde$values, model = "NP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = cp.scale.kde$grid_points, values = cp.scale.kde$values, model = "CP", param = "scale") %>% 
  bind_rows(., data.frame(grid_points = pp.scale.kde$grid_points, values = pp.scale.kde$values, model = "PP", param = "scale")) %>% 
  bind_rows(., data.frame(grid_points = np.scale.kde$grid_points, values = np.scale.kde$values, model = "NP", param = "scale"))) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) -> kerneldata

@@

### EVD generalized pareto results

```{r}
library(extRemes)

```{r fig.show='hide'}

nint <- 70 # number of intervals. how many thresholds to try
r <- c(0, 700) # range over which to try the thresholds
nsamps <- 500 # random sample form the distances

cp.df %>%
  drop_na(., s.id) %>%
  sample_n(., nsamps) -> cp.evd

cp_threshplot <- threshrange.plot(cp.evd$disp, r = r, type = "GP", nint = nint)

```{r}
as.data.frame(cp_threshplot) %>%
  mutate(u.i = seq(r[1], r[2], length.out = nint)) -> cp_threshplot

```{r}
a <- read.table("Ch1_movement_rates/dispdistancestest.txt")
a

threshrange.plot(a$V1, type = "GP", nint = 100, r = c(0,700))
c <- mrlplot(a$V1)
mrlplot(a$V1)

max(c[,3])

b <- decluster(a$V1, threshold = 170)

threshrange.plot(b)

fevd(b, threshold = 170, type = "GP")

as.data.frame(c) -> d

model <- lm(d$`Mean Excess`~1)
confint(model, level = 0.9)
